\propertitle

### 2020-03-16 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T14:36:02+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

%\newcommand*{\suchthat}{\mid}%{\mathpunct{|}}%such that (eg in sets)

@@

%\DeclarePairedDelimiter\opop{]}{[}

@@

%\DeclarePairedDelimiterX{\conds}[2]{\{}{\}}{#1\nonscript\,\delimsize\vert\nonscript\;\mathopen{}#2}

@@

There are many differing views on the questions of comparison, complexity,
nesting, and \enquote{penalization} of models. Our view is close to that
expressed in several works, studies, and commentaries
\citep[\eg][]{good1985,jonesetal1986,chatfield1995,copasetal1995,draper1995,spiegelhalteretal1995,raftery1995,gelmanetal1995,draperetal1996,hoetingetal1999,clydeetal1999,browneetal2006},
and well-explained in MacKay \citey{mackay1992}. We summarize this view
below. According to it, the analysis in our \sect~4, based on the weight of
evidence, is consistent and does not need any corrections.

@@

If a \emph{choice} among two or more hypotheses has to be made for some
purpose (say, hardware algorithm implementation in some automated device),
such choice requires not only the probabilities $p(H_{i}\|D)$, but also the
gain/loss matrix for the various choices conditional on the various
hypotheses. The choice is then made by maximization of the expected gain.
Some gain matrices can even lead to choosing the hypothesis having
\emph{lower} posterior probability \citep[this frequently happens in
medical decision problems, see \eg][]{soxetal1988_r2013}.

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T16:48:19+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

\newcommand*{\suchthat}{\mid}%{\mathpunct{|}}%such that (eg in sets)

@@

\DeclarePairedDelimiter\opop{]}{[}

@@

\DeclarePairedDelimiterX{\conds}[2]{\{}{\}}{#1\nonscript\,\delimsize\vert\nonscript\;\mathopen{}#2}

@@

There are many differing, fragmented views on the questions of comparison,
complexity, nesting, and \enquote{penalization} of models. Our view is
close to that expressed in several works, studies, and commentaries
\citep[\eg][]{good1950,good1985,kadaneetal1980b,jonesetal1986,chatfield1995,copasetal1995,draper1995,spiegelhalteretal1995,raftery1995,gelmanetal1995,mackay1995_r2003,draperetal1996,hoetingetal1999,clydeetal1999,browneetal2006},
and well-explained in MacKay \citey{mackay1992}. We summarize this view
below. According to it, the analysis in our \sect~4, based on the weight of
evidence, is consistent and does not need any corrections.

@@

If a \emph{choice} among two or more hypotheses has to be made for some
purpose (say, hardware algorithm implementation in some automated device),
such choice requires not only the probabilities $\p(H_{i}\|D)$, but also
the utility/loss matrix for the various choices conditional on the various
hypotheses \citep{kadaneetal1980b}. The choice is then made by maximization
of the expected utility, a procedure dictated by some simple rational
desiderata
\citep{fishburn1981,bernardoetal1994_r2000}[\chap~13]{jaynes1994_r2003}.
Some utility matrices can even lead to choosing the hypothesis having
\emph{lower} posterior probability \citep[this frequently happens in
medical decision problems, see \eg][]{soxetal1988_r2013}.

@@

From our Bayesian point of view, the question of comparing (as opposed to
choosing, see above) two models or hypotheses $M_{i}$ is nothing else than
the calculation of their post-data probabilities $\p(M_{i} \| D, I)$, where
$I$ denotes the context and prior information. Such calculation depends on
what we mean by \enquote{model}. There are two main possibilities: model as
a family, or model as a specific distribution.

\smallskip

\textbullet\ If by \enquote{model} we mean only a family of probability
distribution, \eg\
\[\conds*{\exp\biggl[-\frac{(x-\mu)^{2}}{2\sigma^{2}}\biggr]\,\di x}{
    \mu\in\RR, \sigma \in\opop{0,\infty}}\;,\]
then model comparison is undefined, because we cannot calculate
$\p(D \| M_{i})$. Each distribution in the family assigns a different
probability, and it is not clear which should be chosen or how they should
be combined and why. A hypothesis is ill-defined, or at least useless, if
it does not allow us to assign a probability to the data. We need a
pre-data probability distribution for the model parameters, \eg\
$\pf(\mu,\sigma \| I)\,\di\mu\,\di\sigma$. \enquote{Model} must therefore
be redefined as a family of distributions \emph{and} a pre-data
distribution over such family. This redefinition has several consequences:

First, two models are different if they have the same family but different
distributions over it. In fact they lead to different probabilities on the
data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use the one family
distribution \emph{and} the other family distribution at the same time.
It's either-or. This indeed makes sense from a nonparametric perspective,
where a parametric model (in the redefined sense) is just a singular
nonparametric distribution, concentrated on a lower-dimensional manifold
(the family above) of the full space of distributions
\citep[p.~761]{draperetal1996}.

Second, the \enquote{complexity} of a model cannot be simply judged from
the dimensionality of its family. Model $M_{1}$ can have a family
distribution concentrated on a very small region, with respect to model
$M_{2}$ with the same family. $M_{1}$ is thus effectively using
\enquote{fewer} parameters than $M_{2}$. Correspondingly the
\enquote{typical set} of data to which $M_{1}$ assigns appreciable
probability is smaller than the typical set of $M_{2}$: model $M_{1}$ is
\enquote{less powerful}. The effective dimensionality or complexity of a
model is thus best defined by the volume of data that is typical under that
model. It may thus happen that a model is more powerful than another even
if it is defined on a lower-dimensional family.

Third, \emph{the evidence $\p(D \| M_{i}, I)$ of a model automatically
  takes care of its complexity}. This happens because the probability over
the data space is normalized. If $M_{1}$ has a typical data volume larger
than $M_{2}$, then it must also assign lower probability to each data point
in that volume, to ensure normalization. As a result, if the observed data
$D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{1},I)< \pf(D^{*} \| M_{2}, I)$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the data is for each model and each model's
power. This is the so-called automatic Ockham razor of Bayes's theorem,
extensively explained by MacKay \citey{mackay1992}. And this is the reason
why we are personally satisfied with simply comparing the evidence for any
two models.

\smallskip

\textbullet\
